Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-08-10 man/figures/browning.Rmd
change legend
fix typo error

**Figure 3.** Percentage of pixels showing browning, greenning or no-changes during the 2005 and 2012 drought events according to EVI standardized anomalies.

>>>>

**Figure 3.** Percentage of pixels showing browning, greening or no-changes during the 2005 and 2012 drought events according to EVI standardized anomalies. See main text for an explanation of greening and browning.
